---
title: "Daily report"
output: 
  html_document:
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='images/',
                      echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE)
```

```{r sourcing}

setwd("..")
source("global.R")
# OBS <- OBS
# model_1 <- HBV_2014
# model_2 <- HBV_2016
# model_3 <- DDD
```

# Main maps

Below are some maps summarizing the current flooding situation as well as flooding risk for the coming week.

## Current flow

The map below plots for each flood forecasting station, the ratio of current discharge by the mean annual flood

```{r single_station_map, fig.cap='Map of Norway with all stations used for flood forecasting',}
single_station_map(stations, selected_nbname = "2.11-narsjo")
```

## Flood warning ratio

The map below plots for each flood forecasting station, the ratio of current discharge by the mean annual flood

## Uncertainty ratio

The map below plots for each flood forecasting station, the ratio of current discharge by the mean annual flood

# Multimodel plots

Multi-model plot for all stations.

```{r defining_variables}

# selected_nbname <- "2.11-narsjo"

# variable_1 <- c("SimRaw", "SimCorr", "SimL50", "SimH50")
# variable_2 <- c("SimRaw", "SimCorr", "SimP50")
# variable_3 <- c("DDD.Sim", "Obs")  

plot_list <- htmltools::tagList()
stations <- unique(HBV_2014$nbname)
```


```{r multimodel_plots, results = "asis", fig.height= 10, fig.width= 15, fig.keep = "all",, fig.align='center'}

for (i in seq_along(stations)) {

subset2plot_m1 <- dplyr::filter(HBV_2014, nbname == stations[i] & Type == "Runoff") 
subset2plot_m2 <- dplyr::filter(HBV_2016, nbname == stations[i] & Type == "Runoff") 
# subset2plot_m3 <- dplyr::filter(model_3, nbname == stations[i] & Type == "Runoff") 
# subset2plot_obs <- dplyr::filter(OBS, nbname == stations[i] & Variable == "Obs") 

cat("\n## Station ", as.character(stations[i]), "  \n")     
d <- multimod_forecast_plot(obs_data = NULL, dat_1 = NULL, subset2plot_m2, gg_plot = TRUE)
plot(d)
cat('\n') 

}

```

Blabla

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:single_station_map). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
