---
title: "Daily report"
output: 
  html_document:
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}

setwd("..")
source("global.R")
model_1 <- HBV_2014
model_2 <- HBV_2016
model_3 <- DDD
```

# Main maps

Below are some maps summarizing the current flooding situation as well as flooding risk for the coming week.

## Current flow

The map below plots for each flood forecasting station, the ratio of current discharge by the mean annual flood

```{r echo=FALSE, message=FALSE, warning=FALSE}
single_station_map(stations, selected_nbname = "2.11-narsjo")
```

## Flood warning ratio

The map below plots for each flood forecasting station, the ratio of current discharge by the mean annual flood

```{r echo=FALSE, message=FALSE, warning=FALSE}
single_station_map(stations, selected_nbname = "2.11-narsjo")
```

## Uncertainty ratio

The map below plots for each flood forecasting station, the ratio of current discharge by the mean annual flood

```{r echo=FALSE, message=FALSE, warning=FALSE}
single_station_map(stations, selected_nbname = "2.11-narsjo")
```

# Multimodel plots

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.
Interative plots for a few stations

```{r echo=FALSE, eval=TRUE, message=FALSE, warning=TRUE, results = "asis", fig.height= 10, fig.width= 15, fig.keep = "all"}

# selected_nbname <- "2.11-narsjo"

variable_1 <- c("SimRaw", "SimCorr", "SimL50", "SimH50")
variable_2 <- c("SimRaw", "SimCorr", "SimP50")
variable_3 <- c("DDD.Sim", "Obs")  

plot_list <- htmltools::tagList()
stations <- unique(HBV_2014$nbname)
```

```{r echo=FALSE, eval=FALSE, message=FALSE, warning=TRUE, results = "asis", fig.height= 10, fig.width= 15, fig.keep = "all"}

for (i in seq_along(stations)) {

subset2plot_m1 <- dplyr::filter(model_1, nbname == stations[i] & Type == "Runoff" & Variable %in% variable_1) 
subset2plot_m2 <- dplyr::filter(model_2, nbname == stations[i] & Type == "Runoff" & Variable %in% variable_2) 
# subset2plot_m3 <- dplyr::filter(model_3, nbname == stations[i] & Type == "Runoff" & Variable %in% variable_3) 
# subset2plot_m1 <- dplyr::filter(model_1, nbname %in% station & Type == "Runoff" & Variable %in% variable_1)             
#                choices = unique(filter(model_4, Type == "Runoff")$Variable), multiple = TRUE) 
# c("Obs", "Sim"), multiple = TRUE) 
# subset2plot_rl <- dplyr::filter(return_levels, nbname %in% station & Type %in% type_rl) 
      
plot_list[[i]] <- multimod_forecast_plot(subset2plot_m1, subset2plot_m2)

}
plot_list

```

List of static plots for a few stations:

```{r echo=FALSE, message=FALSE, warning=FALSE, results = "asis", fig.height= 10, fig.width= 15, fig.keep = "all"}

for (i in seq_along(stations)) {

subset2plot_m1 <- dplyr::filter(model_1, nbname == stations[i] & Type == "Runoff" & Variable %in% variable_1) 
subset2plot_m2 <- dplyr::filter(model_2, nbname == stations[i] & Type == "Runoff" & Variable %in% variable_2) 
# subset2plot_m3 <- dplyr::filter(model_3, nbname == stations[i] & Type == "Runoff" & Variable %in% variable_3) 

cat("\n## Station ", as.character(stations[i]), "  \n")     
d <- multimod_forecast_plot(subset2plot_m1, subset2plot_m2, gg_plot = TRUE)
plot(d)
cat('\n') 

}


```

Blabla



```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
