<h1>A list a functions to support the Flomvarsling Shiny app</h1>

<p><strong>Authors:</strong> <a href="mailto:fbaffie@gmail.com">Florian Kobierska Baffie</a> [aut, cre]</p>
<p><strong>Version:</strong> 0.1</p>
<p><strong>License:</strong> see license.md</p>

<h4>Description</h4>
<p>This package was developed for the FlomKart project.
It contains functions used by the shiny app</p>



<h4>Imports</h4>
<p>
leaflet,
tidyverse</p>

<h4>Suggests</h4>
<p>
testthat,
packagedocs</p>



  ```{r packagedocs_load_library, echo=FALSE}
  suppressWarnings(suppressMessages(
    library(FlomvarslingApp,
      quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE
    )
  ))
  ```
  

# Package Functions





## dygraph_mod

<a id="dygraph_mod_alias"></a><h3>dygraph_mod</h3>

<p class="rd-p">This was an attempt to modularize Bymans functions. Server module. May not work...</p>

<h4>Usage</h4>
<pre class="r"><code><div>dygraph_mod(input, output, session, selected_stations, model_1, model_2, model_3, model_4&nbsp;=&nbsp;NULL)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>output</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>session</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>selected_stations</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_1</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_2</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_3</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_4</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
</dl>







## dygraph_mod2

<a id="dygraph_mod2_alias"></a><h3>dygraph_mod2</h3>

<p class="rd-p">This was an attempt to modularize Bymans functions. Server module. May not work...</p>

<h4>Usage</h4>
<pre class="r"><code><div>dygraph_mod2(input, output, session, selected_stations, model_1, model_2, model_3, model_4&nbsp;=&nbsp;NULL)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>output</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>session</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>selected_stations</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_1</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_2</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_3</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_4</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
</dl>







## dygraph_modUI

<a id="dygraph_modUI_alias"></a><h3>dygraph_modUI</h3>

<p class="rd-p">This was an attempt to modularize Bymans functions. UI module to be used with "dygraph_mod". May not work...</p>

<h4>Usage</h4>
<pre class="r"><code><div>dygraph_modUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. UI module to be used with "dygraph_mod". May not work...</dd>
</dl>







## forecast_plot

<a id="forecast_plot_alias"></a><h3>forecast_plot</h3>


<h4>Usage</h4>
<pre class="r"><code><div>forecast_plot(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd"></dd>
</dl>







## forecast_plot_mod

<a id="forecast_plot_mod_alias"></a><h3>forecast_plot_mod</h3>

<p class="rd-p">Shiny server module to plot ...</p>

<h4>Usage</h4>
<pre class="r"><code><div>forecast_plot_mod(input, output, session, map_input, dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to plot ...</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to plot ...</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to plot ...</dd>
  <dt>map_input</dt>
  <dd class="rd-dd">Shiny server module to plot ...</dd>
  <dt>dat</dt>
  <dd class="rd-dd">Shiny server module to plot ...</dd>
</dl>







## forecast_plot_mod_shading

<a id="forecast_plot_mod_shading_alias"></a><h3>forecast_plot_mod_shading</h3>

<p class="rd-p">Shiny server module to plot ...
Same plot as forecast_plot_mod but without plotly to get the shading for the current day</p>

<h4>Usage</h4>
<pre class="r"><code><div>forecast_plot_mod_shading(input, output, session, map_input, dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny server module to plot ...
Same plot as forecast_plot_mod but without plotly to get the shading for the current day</dd>
</dl>







## forecast_plot_mod_shadingUI

<a id="forecast_plot_mod_shadingUI_alias"></a><h3>forecast_plot_mod_shadingUI</h3>

<p class="rd-p">Shiny UI module to be used with "forecast_plot_mod_shading"</p>

<h4>Usage</h4>
<pre class="r"><code><div>forecast_plot_mod_shadingUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to be used with "forecast_plot_mod_shading"</dd>
</dl>







## forecast_plot_modUI

<a id="forecast_plot_modUI_alias"></a><h3>forecast_plot_modUI</h3>

<p class="rd-p">Shiny UI module to plot ...</p>

<h4>Usage</h4>
<pre class="r"><code><div>forecast_plot_modUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to plot ...</dd>
</dl>







## forecast_plot_shading

<a id="forecast_plot_shading_alias"></a><h3>forecast_plot_shading</h3>

<p class="rd-p">This function only produces "static" ggplot for the moment, but I need to find a way to do the shading with plotly</p>

<h4>Usage</h4>
<pre class="r"><code><div>forecast_plot_shading(dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat</dt>
  <dd class="rd-dd">This function only produces "static" ggplot for the moment, but I need to find a way to do the shading with plotly</dd>
</dl>


<h4>Examples</h4>
```{r forecast_plot_shading_id_9, eval = TRUE }
# forecast_plot_shading(Mistake, Mist)
# This is dummy example
```





## mapModule

<a id="mapModule_alias"></a><h3>mapModule</h3>

<p class="rd-p">Shiny server module to map ...</p>

<h4>Usage</h4>
<pre class="r"><code><div>mapModule(input, output, session)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to map ...</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to map ...</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to map ...</dd>
</dl>







## mapModule_polygonFeature

<a id="mapModule_polygonFeature_alias"></a><h3>mapModule_polygonFeature</h3>

<p class="rd-p">Shiny server module to map ...</p>

<h4>Usage</h4>
<pre class="r"><code><div>mapModule_polygonFeature(input, output, session)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to map ...</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to map ...</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to map ...</dd>
</dl>







## mapModule_polygonFeatureUI

<a id="mapModule_polygonFeatureUI_alias"></a><h3>mapModule_polygonFeatureUI</h3>

<p class="rd-p">Shiny UI module to be used with "mapModule_polygonFeature" ...</p>

<h4>Usage</h4>
<pre class="r"><code><div>mapModule_polygonFeatureUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to be used with "mapModule_polygonFeature" ...</dd>
</dl>







## mapModuleUI

<a id="mapModuleUI_alias"></a><h3>mapModuleUI</h3>

<p class="rd-p">Shiny UI module to be used with "mapModule" ...</p>

<h4>Usage</h4>
<pre class="r"><code><div>mapModuleUI(id, multiple_choice&nbsp;=&nbsp;FALSE)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to be used with "mapModule" ...</dd>
  <dt>multiple_choice</dt>
  <dd class="rd-dd">Shiny UI module to be used with "mapModule" ...</dd>
</dl>







## multimod_forecast_plot

<a id="multimod_forecast_plot_alias"></a><h3>multimod_forecast_plot</h3>


<h4>Usage</h4>
<pre class="r"><code><div>multimod_forecast_plot(dat_1&nbsp;=&nbsp;NULL, dat_2&nbsp;=&nbsp;NULL, dat_3&nbsp;=&nbsp;NULL, dat_4&nbsp;=&nbsp;NULL, return_levels&nbsp;=&nbsp;NULL, gg_plot&nbsp;=&nbsp;FALSE)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat_1</dt>
  <dd class="rd-dd"></dd>
  <dt>dat_2</dt>
  <dd class="rd-dd"></dd>
  <dt>dat_3</dt>
  <dd class="rd-dd"></dd>
  <dt>dat_4</dt>
  <dd class="rd-dd"></dd>
  <dt>return_levels</dt>
  <dd class="rd-dd"></dd>
  <dt>gg_plot</dt>
  <dd class="rd-dd"></dd>
</dl>







## multimod_forecast_plot_EXP

<a id="multimod_forecast_plot_EXP_alias"></a><h3>multimod_forecast_plot_EXP</h3>

<p class="rd-p">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</p>

<h4>Usage</h4>
<pre class="r"><code><div>multimod_forecast_plot_EXP(dat_1&nbsp;=&nbsp;NULL, dat_2&nbsp;=&nbsp;NULL, dat_3&nbsp;=&nbsp;NULL, dat_4&nbsp;=&nbsp;NULL)</div>
<div>multimod_forecast_plot_EXP(dat_1&nbsp;=&nbsp;NULL, dat_2&nbsp;=&nbsp;NULL, dat_3&nbsp;=&nbsp;NULL, dat_4&nbsp;=&nbsp;NULL)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>dat_1</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>dat_2</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>dat_3</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>dat_4</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>selected_stations</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>model_1</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>model_2</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>model_3</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
  <dt>model_4</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with other functions...
To tidy up probable double up with multimod_forecast_plot</dd>
</dl>







## multimod_forecast_plot_mod

<a id="multimod_forecast_plot_mod_alias"></a><h3>multimod_forecast_plot_mod</h3>

<p class="rd-p">Shiny server module to do multi-model plots. Needs new parametrization!</p>

<h4>Usage</h4>
<pre class="r"><code><div>multimod_forecast_plot_mod(input, output, session, map_input, model_1, model_2, model_3, model_4, return_levels&nbsp;=&nbsp;NULL)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>map_input</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>model_1</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>model_2</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>model_3</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>model_4</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
  <dt>return_levels</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs new parametrization!</dd>
</dl>







## multimod_forecast_plot_modUI

<a id="multimod_forecast_plot_modUI_alias"></a><h3>multimod_forecast_plot_modUI</h3>

<p class="rd-p">Shiny UI module to be used with multimod_forecast_plot</p>

<h4>Usage</h4>
<pre class="r"><code><div>multimod_forecast_plot_modUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to be used with multimod_forecast_plot</dd>
</dl>







## multimod_forecast_selection_modUI

<a id="multimod_forecast_selection_modUI_alias"></a><h3>multimod_forecast_selection_modUI</h3>

<p class="rd-p">Shiny UI module...</p>

<h4>Usage</h4>
<pre class="r"><code><div>multimod_forecast_selection_modUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module...</dd>
</dl>







## multiple_station_map

<a id="multiple_station_map_alias"></a><h3>multiple_station_map</h3>

<p class="rd-p">mapping function</p>

<h4>Usage</h4>
<pre class="r"><code><div>multiple_station_map(stations, selected_regine_main&nbsp;=&nbsp;NULL, selected_name&nbsp;=&nbsp;NULL, selected_long&nbsp;=&nbsp;NULL, selected_lat&nbsp;=&nbsp;NULL, single_poly&nbsp;=&nbsp;FALSE, variable2plot&nbsp;=&nbsp;"none", radius_function&nbsp;=&nbsp;TRUE, popups&nbsp;=&nbsp;FALSE)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>stations</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>selected_regine_main</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>selected_name</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>selected_long</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>selected_lat</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>single_poly</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>variable2plot</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>radius_function</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>popups</dt>
  <dd class="rd-dd">mapping function</dd>
</dl>







## mydygraphModule

<a id="mydygraphModule_alias"></a><h3>mydygraphModule</h3>

<p class="rd-p">This was an attempt to modularize Bymans functions. Server module. May not work...</p>

<h4>Usage</h4>
<pre class="r"><code><div>mydygraphModule(input, output, session)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>output</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>session</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
</dl>







## mydygraphModuleUI

<a id="mydygraphModuleUI_alias"></a><h3>mydygraphModuleUI</h3>

<p class="rd-p">This was an attempt to modularize Bymans functions. UI module to be used with "mydygraphModule". May not work...</p>

<h4>Usage</h4>
<pre class="r"><code><div>mydygraphModuleUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. UI module to be used with "mydygraphModule". May not work...</dd>
</dl>







## NEW_mapModule_polygonFeature

<a id="NEW_mapModule_polygonFeature_alias"></a><h3>NEW_mapModule_polygonFeature</h3>

<p class="rd-p">Shiny server module to map... TO tidy up with mapModule_polygonFeature</p>

<h4>Usage</h4>
<pre class="r"><code><div>NEW_mapModule_polygonFeature(input, output, session)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to map... TO tidy up with mapModule_polygonFeature</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to map... TO tidy up with mapModule_polygonFeature</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to map... TO tidy up with mapModule_polygonFeature</dd>
</dl>







## NEW_mapModule_polygonFeatureUI

<a id="NEW_mapModule_polygonFeatureUI_alias"></a><h3>NEW_mapModule_polygonFeatureUI</h3>

<p class="rd-p">Shiny UI module to be used with "NEW_mapModule_polygonFeature"</p>

<h4>Usage</h4>
<pre class="r"><code><div>NEW_mapModule_polygonFeatureUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to be used with "NEW_mapModule_polygonFeature"</dd>
</dl>







## OLD_forecast_plot_modUI

<a id="OLD_forecast_plot_modUI_alias"></a><h3>OLD_forecast_plot_modUI</h3>

<p class="rd-p">Shiny UI module to plot ...</p>

<h4>Usage</h4>
<pre class="r"><code><div>OLD_forecast_plot_modUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to plot ...</dd>
</dl>







## OLD_mapModule_polygonFeature

<a id="OLD_mapModule_polygonFeature_alias"></a><h3>OLD_mapModule_polygonFeature</h3>

<p class="rd-p">Shiny server module to map... TO tidy up with mapModule_polygonFeature</p>

<h4>Usage</h4>
<pre class="r"><code><div>OLD_mapModule_polygonFeature(input, output, session)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to map... TO tidy up with mapModule_polygonFeature</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to map... TO tidy up with mapModule_polygonFeature</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to map... TO tidy up with mapModule_polygonFeature</dd>
</dl>







## OLD_mapModule_polygonFeatureUI

<a id="OLD_mapModule_polygonFeatureUI_alias"></a><h3>OLD_mapModule_polygonFeatureUI</h3>

<p class="rd-p">Shiny UI module to be used with "OLD_mapModule_polygonFeature"</p>

<h4>Usage</h4>
<pre class="r"><code><div>OLD_mapModule_polygonFeatureUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to be used with "OLD_mapModule_polygonFeature"</dd>
</dl>







## OLD_multimod_forecast_plot

<a id="OLD_multimod_forecast_plot_alias"></a><h3>OLD_multimod_forecast_plot</h3>

<p class="rd-p">Shiny server module to do multi-model plots. Needs tidy up with previous function</p>

<h4>Usage</h4>
<pre class="r"><code><div>OLD_multimod_forecast_plot(input, output, session, selected_stations&nbsp;=&nbsp;NULL, model_1, model_2, model_3, model_4, return_levels&nbsp;=&nbsp;NULL, variable_1, variable_2, variable_3, variable_4, type_rl)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>selected_stations</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>model_1</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>model_2</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>model_3</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>model_4</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>return_levels</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>variable_1</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>variable_2</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>variable_3</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>variable_4</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
  <dt>type_rl</dt>
  <dd class="rd-dd">Shiny server module to do multi-model plots. Needs tidy up with previous function</dd>
</dl>







## single_station_map

<a id="single_station_map_alias"></a><h3>single_station_map</h3>

<p class="rd-p">mapping function</p>

<h4>Usage</h4>
<pre class="r"><code><div>single_station_map(stations, selected_nbname&nbsp;=&nbsp;NULL, selected_long&nbsp;=&nbsp;NULL, selected_lat&nbsp;=&nbsp;NULL, variable2plot&nbsp;=&nbsp;"none", map_layer&nbsp;=&nbsp;"open streetmap", catchments&nbsp;=&nbsp;FALSE, colored_markers&nbsp;=&nbsp;FALSE, radius_function&nbsp;=&nbsp;TRUE, popups&nbsp;=&nbsp;FALSE)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>stations</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>selected_nbname</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>selected_long</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>selected_lat</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>variable2plot</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>map_layer</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>catchments</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>colored_markers</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>radius_function</dt>
  <dd class="rd-dd">mapping function</dd>
  <dt>popups</dt>
  <dd class="rd-dd">mapping function</dd>
</dl>







## table_mod

<a id="table_mod_alias"></a><h3>table_mod</h3>

<p class="rd-p">Shiny server module to render data tables</p>

<h4>Usage</h4>
<pre class="r"><code><div>table_mod(input, output, session, dat)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">Shiny server module to render data tables</dd>
  <dt>output</dt>
  <dd class="rd-dd">Shiny server module to render data tables</dd>
  <dt>session</dt>
  <dd class="rd-dd">Shiny server module to render data tables</dd>
  <dt>dat</dt>
  <dd class="rd-dd">Shiny server module to render data tables</dd>
</dl>







## table_modUI

<a id="table_modUI_alias"></a><h3>table_modUI</h3>

<p class="rd-p">Shiny UI module to be used with table_mod</p>

<h4>Usage</h4>
<pre class="r"><code><div>table_modUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">Shiny UI module to be used with table_mod</dd>
</dl>







## taylor_mod

<a id="taylor_mod_alias"></a><h3>taylor_mod</h3>

<p class="rd-p">This was an attempt to modularize Bymans functions. Server module. May not work...</p>

<h4>Usage</h4>
<pre class="r"><code><div>taylor_mod(input, output, session, selected_stations, model_1, model_2, model_3, model_4&nbsp;=&nbsp;NULL)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>input</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>output</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>session</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>selected_stations</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_1</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_2</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_3</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
  <dt>model_4</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. Server module. May not work...</dd>
</dl>







## taylor_modUI

<a id="taylor_modUI_alias"></a><h3>taylor_modUI</h3>

<p class="rd-p">This was an attempt to modularize Bymans functions. UI module to be used with "taylor_mod". May not work...</p>

<h4>Usage</h4>
<pre class="r"><code><div>taylor_modUI(id)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>id</dt>
  <dd class="rd-dd">This was an attempt to modularize Bymans functions. UI module to be used with "taylor_mod". May not work...</dd>
</dl>







## which_station_in_polygon

<a id="which_station_in_polygon_alias"></a><h3>which_station_in_polygon</h3>

<p class="rd-p">Sub-function use to find which stations are in the polygon the user has drawn</p>

<h4>Usage</h4>
<pre class="r"><code><div>which_station_in_polygon(stations, map_selection)</div></code></pre>

<h4>Arguments</h4>
<dl class="rd-dl">
  <dt>stations</dt>
  <dd class="rd-dd">Sub-function use to find which stations are in the polygon the user has drawn</dd>
  <dt>map_selection</dt>
  <dd class="rd-dd">Sub-function use to find which stations are in the polygon the user has drawn</dd>
</dl>



